HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-08-01 scnn.tex
added caption to example maps

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\linewidth}
        \centering
        \includegraphics[width=\linewidth]{exampleEarthTopo}
        \caption{}
        \label{fig:example_earth}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\linewidth}
        \centering
        \includegraphics[width=\linewidth]{exampleCMB}
        \caption{}
        \label{fig:example_cmb}
    \end{subfigure}
    \caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
    \label{fig:example_maps}
\end{figure}

>>>>

\begin{figure*}
\includegraphics[width=\linewidth]{figures/figure_example_maps.pdf}
\caption{Exmaple maps on the sphere:
(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
These maps were pixelised using \texttt{nside}=512.
The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
}
\label{fig:example_maps}
\end{figure*}

% \begin{figure}
%     \centering
%     \begin{subfigure}[b]{0.45\linewidth}
%         \centering
%         \includegraphics[width=\linewidth]{exampleEarthTopo}
%         \caption{}
%         \label{fig:example_earth}
%     \end{subfigure}
%     \hfill
%     \begin{subfigure}[b]{0.45\linewidth}
%         \centering
%         \includegraphics[width=\linewidth]{exampleCMB}
%         \caption{}
%         \label{fig:example_cmb}
%     \end{subfigure}
%     \caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
%     \label{fig:example_maps}
% \end{figure}
